### 2014-09-20 paper.tex
updated some citations and figure description

Reads from each dataset were mapped to transcripts from the gene models using
Bowtie version 1.0.0. The parameter is set for Bowtie to report up to 100
alignments per read.  Reads mapped across exon junctions from all datasets were
counted using Samtools\cite{Li:2009vz} and Pysam\cite{pysam}.

@@

\begin{figure}[!ht]
\begin{center}
\includegraphics[width=5in]{mouse_venn.pdf}
\end{center}
\caption{
{\bf Splice sites in mouse Ensembl gene models, Cufflinks and the \emph{de novo}
assembly pipeline.} In contrast to chicken datasets, Cufflinks and the pipeline
detects the similar amount of non-overlapped annotated junctions.}
\label{mus_venn}
\end{figure}

>>>>

Reads from each dataset were mapped to transcripts from the gene models using
Bowtie version 1.0.0. The parameter is set for Bowtie to report up to 100
alignments per read.  Reads mapped across exon junctions from all datasets were
counted using Samtools\cite{li2009sequence} and Pysam\cite{pysam}.

@@

\begin{figure}[!ht]
\begin{center}
\includegraphics[width=5in]{mouse_venn.pdf}
\end{center}
\caption{
{\bf Splice sites in mouse Ensembl gene models, Cufflinks and the \emph{de
novo} assembly pipeline.} In contrast to chicken datasets, 85,160 (96.8\%) of
splice junctions found by Cufflinks are annotated in mouse ENSEMBL models. The
higher percentage of ENSEMBL splice junctions found by Cufflinks may be a
result of more complete ENSEMBL gene models. While Gimme can detect the similar
number of ENSEMBL splice junctions, it detects many more non-ENSEMBL splice
junctions in mouse.}
\label{mus_venn}
\end{figure}
